---
title: "Datamining Project"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css : styles.css
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
library(flexdashboard)
data=read.csv("HR_comma_sep.csv", sep=",")
#View(data)
#str(data)
#summary(data)
#df_scaled = scale(data[,1:8])
#df_scaled = cbind.data.frame(df_scaled , data$salary)
#View(df_scaled)
#colnames(df_scaled)[9] = "salary"
#df_scaled$salary = as.character(df_scaled$salary)
#df_scaled$salary[df_scaled$salary=='low']<-"0"
#df_scaled$salary[df_scaled$salary=='medium']<-"0"
#df_scaled$salary[df_scaled$salary=='high']<-"1"
#df_scaled$salary =as.factor(df_scaled$salary)
#attach(data)
#for ( i in 7:10) {
#   data[,i] <- as.factor(data[,i])
#}
#str(data)
df_scaled = scale(data[,1:8])
df_scaled = cbind.data.frame(df_scaled , data$salary)

View(df_scaled)
colnames(df_scaled)[9] = "salary"
df_scaled$salary = as.character(df_scaled$salary)
df_scaled$salary[df_scaled$salary=='low']<-"0"
df_scaled$salary[df_scaled$salary=='medium']<-"0"
df_scaled$salary[df_scaled$salary=='high']<-"1"
df_scaled$salary =as.factor(df_scaled$salary)
df_scaled1 = as.data.frame(df_scaled)
colnames(df_scaled1)[9] = "salary"
df_scaled1$salary = as.character(df_scaled1$salary)
df_scaled1$salary[df_scaled1$salary=='low']<-"0"
df_scaled1$salary[df_scaled1$salary=='medium']<-"0"
df_scaled1$salary[df_scaled1$salary=='high']<-"1"
df_scaled1$salary =as.numeric(df_scaled1$salary)
dfdf = as.data.frame(df_scaled1)
View(df_scaled1)
attach(data)
for ( i in 7:10) {
   data[,i] <- as.factor(data[,i])
}
left = data[,8]
View(left)
str(data)

library(ggplot2)
library(purrr)
library(tidyr)
library(ggplot2)


#etude univariée #plotly


#library(plotly)
#library(RColorBrewer)
##p <- ggplot(data, aes(x = left)) +
##  geom_bar(fill=c('steelblue', 'red'),size=2) + 
##  ylab("employees") 
#p=ggplot(data=data, aes(x=left)) +geom_bar(stat="count", position=position_dodge(),fill=c('steelblue', #'red'),size=0.5 ,colour="black") + scale_fill_manual(values=c("#999999", "#E69F00"))+ggtitle("How many employees #left/stayed ")+scale_x_discrete(labels = c('Left','Stayed'))
#
#ggplotly(p)  

library(highcharter)
options(highcharter.theme = hc_theme_smpl(tooltip = list(valueDecimals = 2)))
library(dplyr)
table(left)[1]

left0=as.data.frame(sum(table(data$left)[1]))
View(left0)
leftt=as.data.frame(left0)
View(leftt)
View(x)
leftt[2,]=sum(table(data$left)[2])
x3 = c('Didnt Left','Left')
leftt = cbind.data.frame(leftt,x3)
colnames(leftt)[1]="x"
leftt$x3= as.factor(leftt$x3)
leftt$x = as.numeric(leftt$x)
library(dplyr)
library(highcharter)
options(highcharter.theme = hc_theme_monokai())
hc <- leftt %>%
  hchart(
    "pie", hcaes(x = leftt$x3,y= leftt$x),
    name = "Count"
    )%>%
  hc_title(
    text = "How many Employees left",
    style = list(fontWeight = "bold", fontSize = "30px"),
    align = "center"
    )





#department


#par(mfrow=c(1,2))
#dep.plot <- ggplot(data, aes(Department)) + 
#  geom_bar(stat = "Count",fill = brewer.pal(length(unique(Department)), "Set3")
#) +ggtitle("Distribution of employees per department")
#
#ggplotly(dep.plot)
numb = nrow(data)
#library(plotly)
#fig <- plot_ly() 
#fig <- fig %>%
#  add_trace(
#    type = "pie",
#    title="Pie chart of employees distribution per departments",
#    name = "",
#    values =numb,
#    labels = Department,
#    text = Department,
#    hovertemplate = "%{label}: <br>rate: %{percent} </br>")
#
#
#fig
time_spend_company = as.factor(time_spend_company)
#e=ggplot(data, aes(x = factor(time_spend_company,ordered = TRUE))) + geom_bar(stat='count', #fill=c('#f3c5dc','#f3c5c5','#ffdcdc','#fff1c4','#f0ffc4','#d5e8ea','#bfd0e3','#98a6b5')) + #xlab('time_spend_company')
#ggplotly(e)
#
#
#

ded = as.data.frame(data)
ded[,11]= paste("",1:nrow(ded))
colnames(ded)[11]= "id"
View(ded)
table(data$Department)
ded$id = as.numeric(ded$id)
accounting <- ded %>% filter(Department == "accounting")
hr <- ded %>% filter(Department == "hr")
it = ded %>% filter(Department == "IT")
management = ded %>% filter(Department == "management")
marketing = ded %>% filter(Department == "marketing")
product_mng = ded %>% filter(Department == "product_mng")
RandD = ded %>% filter(Department == "RandD")
sales = ded %>% filter(Department == "sales")
support = ded %>% filter(Department == "support")
technical = ded %>% filter(Department == "technical")
View(accounting)
hc1 <- hchart(
  accounting$Department,
  color ="red", name = "accounting"
  ) %>%
  hc_add_series(
    hr$Department,
    color = "blue", 
    name = "hr",
    type = "column"
    )%>%
  hc_add_series(
    it$Department,
    color = "orange", 
    name = "IT",
    type = "column"
    )%>%
  hc_add_series(
    management$Department,
    color = "green", 
    name = "management",
    type = "column"
    )%>%
  hc_add_series(
    marketing$Department,
    color = "yellow", 
    name = "marketing",
    type = "column"
    )%>%
  hc_add_series(
    product_mng$Department,
    color = "purple", 
    name = "product_mng",
    type = "column"
    )%>%
  hc_add_series(
    RandD$Department,
    color = "pink", 
    name = "marketing",
    type = "column"
    )%>%
  hc_add_series(
    sales$Department,
    color = "cyan", 
    name = "sales",
    type = "column"
    )%>%
  hc_add_series(
    support$Department,
    color = "lime", 
    name = "support",
    type = "column"
    )%>%
  hc_add_series(
    technical$Department,
    color = "brown", 
    name = "technical",
    type = "column"
    )%>%
  hc_title(
    text = "Employees per Departement",
    style = list(fontWeight = "bold", fontSize = "30px"),
    align = "center"
    )

  

library(plotly)
#fig <- plot_ly(y = satisfaction_level, type = "box", name="Satisfaction Level")
#fig <- fig %>% add_trace(y = last_evaluation, name="Last Evaluation")
#
#fig
#fig2 <- plot_ly(y = average_montly_hours , type = "box", name="Average Monthly Hours")
#fig2
options(highcharter.theme = hc_theme_google())
hec <- hchart(
  density(ded$satisfaction_level), 
  type = "area", name = "Satisfaction level"
  )%>%
  hc_add_series(
    density(ded$last_evaluation), type = "area",
    color = "#B71C1C", 
    name = "Last evaluation"
    )



data$Work_accident = as.factor(Work_accident)

left2=as.data.frame(sum(table(data$time_spend_company)[1]))
View(left2)
leftt1=as.data.frame(left2)
View(leftt1)
View(x)
leftt1[2,]=sum(table(data$time_spend_company)[2])
leftt1[3,]=sum(table(data$time_spend_company)[3])
leftt1[4,]=sum(table(data$time_spend_company)[4])
leftt1[5,]=sum(table(data$time_spend_company)[5])
leftt1[6,]=sum(table(data$time_spend_company)[6])
leftt1[7,]=sum(table(data$time_spend_company)[7])
leftt1[8,]=sum(table(data$time_spend_company)[8])
x4 = c('2 Years','3 Years','4 Years','5 Years','6 Years','7 Years','8 Years','10 Years')
leftt1 = cbind.data.frame(leftt1,x4)
colnames(leftt1)[1]="x"
leftt1$x4= as.factor(leftt1$x4)
leftt1$x = as.numeric(leftt1$x)
length(leftt1$x)

options(highcharter.theme = hc_theme_ffx())
hc2 <- leftt1 %>%
  hchart(
    "pie", hcaes(x = leftt1$x4,y= leftt1$x),
    name = "Count"
    )%>%
  hc_title(
    text = "Time Spent by the employee in the Company",
    style = list(fontWeight = "bold", fontSize = "30px"),
    align = "center"
    )



#labelss = c('No','Yes')
#workac_plot=ggplot(data=data, aes(x=Work_accident)) +geom_bar(stat="count", #position=position_dodge(),fill=c('steelblue', 'red'),size=0.5 ,colour="black") + #scale_fill_manual(values=c("#999999", "#E69F00"))+ggtitle("Did the employee had an accident? ") + #scale_x_discrete(labels=c('No','Yes'))
#
#ggplotly(workac_plot)  
#promotion_last_5years_plot = ggplot(data=data, aes(x=promotion_last_5years)) +geom_bar(stat="count", #position=position_dodge(),fill=c('steelblue', 'red'),size=0.5 ,colour="black") + #scale_fill_manual(values=c("#999999", "#E69F00"))+ggtitle("Did the employee had a promotion in the last 5 years? #") + scale_x_discrete(labels=c('No','Yes'))
#ggplotly(promotion_last_5years_plot)



#Satisfaction / salaire
#View(df_scaled)
#df2 = cor(df_scaled[,-9])
#df2
#heat_plot = plot_ly (x=colnames(df2),y=colnames(df2),z = df2, type = "heatmap")
#heat_plot
df2 = cor(dfdf)
df2
heat_plot = plot_ly (x=colnames(df2),y=colnames(df2),z = df2, type = "heatmap")
heat_plot
options(highcharter.theme = hc_theme_elementary(tooltip = list(valueDecimals = 2)))
hmap=hchart(df2, type = "heatmap", hcaes(x = colnames(df2), y = colnames(df2), value = df2))%>%
  hc_title(
    text = "Correlation Matrix",
    style = list(fontWeight = "bold", fontSize = "30px"),
    align = "center"
    )


#this heatmap below represent the correlation between our variables. in fact, we have a negative correlation  between left and satisfaction level, which means that the employee left when their  satisfaction level is low 




#test <- plot_ly(ggplot2::diamonds, y = ~average_montly_hours , color = ~left, type = "box")

#test

#corrprom <- plot_ly(ggplot2::diamonds, x = ~promotion_last_5years, y = ~average_montly_hours, color = ~clarity, #type = "box")
#corrprom <- fig %>% layout
#
#corrprom
work0 = ded %>% filter(Work_accident == "0")
work1 = ded %>% filter(Work_accident == "1")
accident0 = ded %>% filter(Work_accident == "0")
accident1 = ded %>% filter(Work_accident == "1")
accident1$Work_accident= as.factor(accident1$Work_accident)
accident0$Work_accident= as.factor(accident0$Work_accident)
options(highcharter.theme = hc_theme_bloom())
hc3 <- hchart(
  accident0$Work_accident,
  color ="red", name = "No accidents"
  ) %>%
  hc_add_series(
    accident1$Work_accident,
    color = "blue", 
    name = "Had an Accident",
    type = "column"
    )%>%
  hc_title(
    text = "Work Accidents",
    style = list(fontWeight = "bold", fontSize = "30px"),
    align = "center"
    )
hc3





#PCA


data2=data
row.names(data2)= paste("employee",1:nrow(data2))
rownames(data2)



library(FactoMineR)
res.pca=PCA(data2,quali.sup =6:10)
# Dimension 1 represents all the efforts that employees put into their work through those variable time spend company , number project , average monthly hours and last evaluation 
#Dimension 2 represents the feeling felt during or after accomplishing the effort previously mentioned in the first dimension 



# to visualize more efficiently the graph of individuals we will proceed with the FactoExtra library 
library(factoextra)
groups=as.factor(Department[1:14999])
fviz_pca_ind(res.pca,
             col.ind = groups, # Habillage par groupes 
             palette=c('#521070','#75892e','#b54e10','#b5002c','#15538c',
                       '#f96a35','#c63d0a','#05d86e','#06934c','#ffc3a0'), 
             addEllipses=TRUE,
             ellips.type="confidence",
             legend.title="Departments",
             repel=TRUE
             ) 

# We can observe a similarity between employees for all departments and the color are inappropriate to differentiate more effectively between ellipses
#=> that's why we will took a couple of ellipses with more pertinent colors to try to distinguish between them 






eclipse1=subset(data2, Department == 'sales'|Department=='management')
eclipse1
nrow(eclipse1)
levels(eclipse1$Department)
eclipse1$Department=as.factor(eclipse1$Department)
troups=as.factor(eclipse1$Department[1:4770])





PCA1=PCA(eclipse1,quali.sup =6:10)
fviz_pca_ind(PCA1,
             col.ind = eclipse1$Department, # Habillage par groupes 
             palette=c('#521070','#b54e10'), 
             addEllipses=TRUE,
             ellips.type="confidence",
             legend.title="Departments",
             repel=TRUE
             )

# sales employees tend to be more satisfied then management employees by the work in the company




eclipse2=subset(data2, Department == 'accounting'|Department=='hr')
eclipse2
nrow(eclipse2)
levels(eclipse2$Department)
eclipse2$Department=as.factor(eclipse2$Department)
PCA2=PCA(eclipse2,quali.sup =6:10)
fviz_pca_ind(PCA2,
             col.ind = eclipse2$Department, # Habillage par groupes 
             palette=c('#521070','#b54e10'), 
             addEllipses=TRUE,
             ellips.type="confidence",
             legend.title="Departments",
             repel=TRUE
             )
#accounting employees tend to have more projects than HR employees



eclipse3=subset(data2, Department == 'IT'|Department=='marketing')
eclipse3
nrow(eclipse3)
levels(eclipse3$Department)
eclipse3$Department=as.factor(eclipse3$Department)
PCA3=PCA(eclipse3,quali.sup =6:10)
fviz_pca_ind(PCA3,
             col.ind = eclipse3$Department, # Habillage par groupes 
             palette=c('#521070','#b54e10'), 
             addEllipses=TRUE,
             ellips.type="confidence",
             legend.title="Departments",
             repel=TRUE
             )
# the 2 ellipses are identicals so we cannot distinguish a noticeable difference between them



eclipse4=subset(data2, Department == 'product_mng'|Department=='RandD')
eclipse4
nrow(eclipse4)
levels(eclipse4$Department)
eclipse4$Department=as.factor(eclipse4$Department)
PCA4=PCA(eclipse4,quali.sup =6:10)
fviz_pca_ind(PCA4,
             col.ind = eclipse4$Department, # Habillage par groupes 
             palette=c('#521070','#b54e10'), 
             addEllipses=TRUE,
             ellips.type="confidence",
             legend.title="Departments",
             repel=TRUE
             )
#product management employees tend to have more projects and have higher evaluation score than R&D 



eclipse5=subset(data2, Department == 'support'|Department=='technical')
eclipse5
nrow(eclipse5)
levels(eclipse5$Department)
eclipse5$Department=as.factor(eclipse5$Department)
PCA5=PCA(eclipse5,quali.sup =6:10)
fviz_pca_ind(PCA5,
             col.ind = eclipse5$Department, # Habillage par groupes 
             palette=c('#521070','#b54e10'), 
             addEllipses=TRUE,
             ellips.type="confidence",
             legend.title="Departments",
             repel=TRUE
             )
#technical employees tend to have more projects and consequently more average monthly hours 


#In order to have the complete perspective of all the variables , we will take a look on the other dimensions  

library(factoextra)
# We have in total 5 dimensions (5 active variables)
res.pca1=PCA(data2,quali.sup =6:10, axes =c(2,3))
res.pca2=PCA(data2,quali.sup =6:10, axes =c(1,3))
# the third dimension for the two figure refers to seniority of the employees in the company 

#inertia Study 

res.pca$eig
res.pca$eig[,1]>1 
# According to Kaiser method => we will keep the 2 first dimension 
get_eig(res.pca)
fviz_screeplot(res.pca) 
# According to the Coude method => the break is not visible , so we can't count on Coude method



#individuals study 

res.pca$ind$coord
which.max(res.pca$ind$coord[,1]) # the 810th employee had the maximum score , in the first dimension that is related to the effort putted in the work , so s/he's the most hardworking one 
data2[810,]

which.min(res.pca$ind$coord[,1]) # the 6885th employee had the minimum score , in the first dimension that is related to the effort putted in the work , so he or she is the laziest one 
data2[6885,]

which.max(res.pca$ind$coord[,2]) # the 2601th employee is the most satisfied one with his/her job in the company 
data2[2601,]

which.min(res.pca$ind$coord[,2]) # 11293th is the most unsatisfied one with his/her job in the company 
data2[11293,]

which.max(res.pca$ind$coord[,3]) # the 11347th employee is the oldest in the company
data2[11347,] 

which.min(res.pca$ind$coord[,3]) # the 11102th is the newest one in the company 
data2[11102,]
# We need to verify for each previous affirmation (exemple)
# which.min(time_spend_company)
# time_spend_company[51]



#Quality of representation of the employees (individuals) by dimensions
res.pca$ind$cos2

# first Dimension 
which.max(res.pca$ind$cos2[,1]) #=> the 10353th employee is the best represented one by the first dimension
which.min(res.pca$ind$cos2[,1]) #=> the 3244 th employee is the less represented one by the first dimension

# Second Dimension 
which.max(res.pca$ind$cos2[,2]) #=> the 11069th employee is the best represented one by the second dimension
which.min(res.pca$ind$cos2[,2]) #=> the 2471 employee is the less represented one by the second dimension

# Third Dimension 
which.max(res.pca$ind$cos2[,3]) #=> the 2472th is the best represented one by the third dimension
which.min(res.pca$ind$cos2[,3]) #=> the 10837th employee is the less represented one by the second dimension




# Contibution of each employee in the construction of the dimensions 
res.pca$ind$contrib

# first Dimension 
which.max(res.pca$ind$contrib[,1]) #=> 810th (check coord)
which.min(res.pca$ind$contrib[,1]) #=> 4038th 

# Second Dimension 
which.max(res.pca$ind$contrib[,2]) #=> 11293th (check coord , most unsatisfied)
which.min(res.pca$ind$contrib[,2]) #=> 2471th 

# Third Dimension 
which.max(res.pca$ind$contrib[,3]) #=> 11347th (check coord , oldest)
which.min(res.pca$ind$contrib[,3]) #=> 10837th 



#variable study 

res.pca$var$cor

res.pca$var$cor[,1]>0.5 #=> most correlated variables with the first dimension 
res.pca$var$cor[,1]<0 #=> inversely correlated variables with the first dimension 

res.pca$var$cor[,2]>0.5 #=> #=> most correlated variables with the second dimension
res.pca$var$cor[,2]<0 #=> inversely correlated variables with the second dimension 

res.pca$var$cor[,3]>0.5 #=> #=> most correlated variables with the third dimension
res.pca$var$cor[,3]<0 #=> inversely correlated variables with the third dimension 




res.pca$var$contrib
#first dimension 
#=>  the variable number_project  contributed the most to the construction of the first dimension 
#=> the variable satisfaction_level contributed the less to the construction of the first dimension

#Second dimension 
#=> the variable satisfaction_level contributed the most to the construction of the second dimension
#=> the variable number_project  contributed the less to the construction of the second dimension 

#third dimension 
#=> the variable time_spend_company contributed the most to the construction of the third dimension
#=> the variable last_evaluation contributed the less to the construction of the third dimension  




#Quality of representation of the variables by dimensions
res.pca$var$cos2

res.pca$var$cos2[,1]>0.5 #=> the first dimension have a good representation of those variables 
res.pca$var$cos2[,2]>0.5 #=> the second dimension have a good representation of those variables 
res.pca$var$cos2[,3]>0.5 #=> the third dimension have a good representation of those variables 




#Considering the fact that half of our variables are factors and consequetly we had to consider them as sup variable. We will take the ACM reduction  method in consideration and see if it's more suitable for our dataset than PCA 
#ACM 

res.acm=MCA(data2,quanti.sup = 1:5)
# Compared to PCA (58% approximately) , the MCA doesn't have significant dimensions with a total of 17,97% 
# => So we will proceed with a PCA as the most practical synthetic information method 


df_scaled
df_scaled$salary = as.numeric(df_scaled$salary)
d1=dist(df_scaled[1:4600,],method="euclidean")
h1=hclust(d1,method="ward.D")
h1$method
h1$dist.method 
h1$height
h1$order
h1$merge
plot(h1)
View(df_scaled)
df_scaled$salary = scale(df_scaled$salary)
rownames(df_scaled) = paste("employee",1:nrow(df_scaled))
df_scaled$salary =as.numeric(df_scaled$salary)
library(clValid)
intern=clValid(df_scaled[1:4600,],2:4,clmethods=c("hierarchical"),validation="internal")
summary(intern)
library(FactoMineR)

classes= cutree(h1,k=2)
classes
View(classes)
table(classes)
d.class=cbind.data.frame(df_scaled[1:4600,],as.factor(classes))
View(d.class)
colnames(d.class)[10]="classes.cah"
catdes(d.class, num.var =10)
library(factoextra)
fviz_cluster(object=list(data = df_scaled[1:4600,], cluster = classes))






kcdeca=kmeans(df_scaled[1:4600,],centers=2,iter.max = 1000)
kcdeca$centers
kcdeca$size
kcdeca$cluster
kcdeca$withinss
d.class=cbind.data.frame(d.class,classes=as.factor(kcdeca$cluster))

colnames(d.class)[11]="classe.kmeans"
View(d.class)
res.cat1 = catdes(d.class,num.var = 11)
res.cat1
intern1=clValid(df_scaled[1:4600,],2:6,clMethods=c("hierarchical","kmeans"), validation= "internal")
summary(intern1)
fviz_cluster(object=list(data = df_scaled[1:4600,], cluster = kcdeca$cluster))




#Decision Tree

View(data)
data_logit = data[,-9]
data_logit = data_logit[,-9]
data_logit = as.data.frame(data_logit)
data_logit = scale(data_logit[,1:5],center= T, scale= T)
data_logit = cbind.data.frame(data_logit,data[,6:8])
data_logit = cbind.data.frame(data_logit,data[,10])
View(data_logit)
colnames(data_logit)[9] = "salary"
data_logit$salary = as.character(data_logit$salary)
data_logit$salary[data_logit$salary=='low']<-"0"
data_logit$salary[data_logit$salary=='medium']<-"0"
data_logit$salary[data_logit$salary=='high']<-"1"
data_logit$salary =as.factor(data_logit$salary)
View(data_logit)
modele_c = glm(data_logit$salary~.,data = data_logit,family = binomial,maxit = 100)
summary(modele_c)
str_constant<-"~1"
str_all<-"~satisfaction_level+last_evaluation+number_project+average_montly_hours+time_spend_company+promotion_last_5years+Work_accident+left"
library(MASS)
#modele.forward<-stepAIC(modele_c,scope = list(lower=str_constant, upper = str_all),trace = T, data = data_logit, direction = "forward")
#summary(modele.forward)  
#modele_complet= glm (salary ~ ., data =data_logit , family= binomial,maxit=100)#modele complet
#summary(modele_complet)
modele.backward = stepAIC(modele_c, ~. , trace=TRUE , data= data_logit, direction  = "backward")
library(rpart)
library(rpart.plot)
View(dataa)
dataa = data[,-9]
dataa = as.data.frame(dataa)
dataa$salary = as.character(dataa$salary)
dataa$salary[dataa$salary=='low']<-"0"
dataa$salary[dataa$salary=='medium']<-"0"
dataa$salary[dataa$salary=='high']<-"1"

dataa$salary =as.factor(dataa$salary)

model.tree<-rpart(salary ~. ,data=dataa[1:2000,],method="class",control=rpart.control(minsplit=5,cp=0))
rpart.plot(model.tree)

```

# Introduction

## Column {data-width=350}

### Introduction

<div class= "alert alert-dismissible alert-danger">
<strong style="color : black">Scope/context : </strong> <a class="alert-link">In the
Presentation Dataset Due to The Great Resignation phenomenon in the USA
which describe elevated rate of workers quitting their job starting in
the spring of 2021 , consequently to the covid crisis and the paradigm
shift that have operated with the new work market reality and its new
approach (remote work , ) , our enterprise search to understand and to
anticipate why employee would and will quit their job , considering the
internal parameters and try submitting again. </a>
</div>

<div class= "alert alert-dismissible alert-danger">
<strong style="color : black">Variables</strong>

<p style="color : black"> <a class="alert-link">Number of project</a> : describe how many
projects did every employee endorse during his working sessions</p>

<p style="color : black"><a class="alert-link">Average_monthly_hours</a>: average of
hours spend at working</p>

<p style="color : black"> <a  class="alert-link">Time_spend_in company</a>: how many
years did the employee spent in the company </p>

<p style="color : black"><a  class="alert-link">Satisfaction level</a>: how much the
employee is satisfied of his/her job</p>

<p style="color : black"> <a  class="alert-link">Left</a>: express if the employee had
or hadn't left the job</p>

<p style="color : black"> <a  class="alert-link">promotion_last_5years</a>: show if
the employee got a promotion in the last 5 years </p>

<p style="color : black"><a class="alert-link">Department</a>: show in which
department the employee is affected/belong</p>

<p style="color : black"> <a  class="alert-link">Salary</a>: Show the level of the
salary for each employee</p>

<p style="color : black"> <a  class="alert-link"> Work_accident</a>: Show if the employee got a work accident before</p>

<p style="color : black"><a class="alert-link">Last evaluation</a>: show the last evaluation that the employee got
from the HR department</p>
</div>

## Column {data-width=650}

### Scoop Of context 

<video width="650" height="500" controls>
  <source src="tl.mp4" type="video/mp4">
</video>

# Exploratory analysis

## Column {.tabset}

### Plot 1

```{r}
hc 
```

>

### Plot 2

```{r}
hc1
```

## Column

### Plot 3

```{r}
hec
```

>

## Column

### Plot 4

```{r}
hc2
```

>

### Plot 5

```{r}
hc3
```

>

# Correlation Matrix

## Column

### Matrix

```{r}
options(highcharter.theme = hc_theme_smpl(tooltip = list(valueDecimals = 2)))
hmap
```

# Advanced Exploratory Analysis

## Column {.tabset}

### Chart 1

```{r}
res.pca=PCA(data2,quali.sup =6:10)
```

>

### Chart 2

```{r}
fviz_pca_ind(res.pca,
             col.ind = groups, # Habillage par groupes 
             palette=c('#521070','#75892e','#b54e10','#b5002c','#15538c',
                       '#f96a35','#c63d0a','#05d86e','#06934c','#ffc3a0'), 
             addEllipses=TRUE,
             ellips.type="confidence",
             legend.title="Departments",
             repel=TRUE
             ) 
```

>

### Chart 3 MCA

```{r}
res.acm=MCA(data2,quanti.sup = 1:5)
```

>

# Unsupervised Clustering

## Column {.tabset}

### CAH

```{r}
fviz_cluster(object=list(data = df_scaled[1:4600,], cluster = classes))
```

>

### Kmeans

```{r}
fviz_cluster(object=list(data = df_scaled[1:4600,], cluster = kcdeca$cluster))
```

>

# Supervised Learning

## Column

### Logit Model

```{r}
summary(modele_c)
```

>

# Decision Tree

## Column

### Decision Tree Plot

```{r}
rpart.plot(model.tree)
```

>